An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-08 main.tex

\usepackage[backend=biber, firstinits=false, backref=false, url=true,
            isbn=true, style=numeric]{biblatex}
\addbibresource{./tex/bibliography.bib}

% Title
\title{An empirical study of fixation for strategies in the
       Iterated Prisoner's Dilemma}
\author{Marc Harper \and Vincent Knight \and Nikoleta E. Glynatsi} % TODO Authors?
\date{}

@@

\begin{abstract}
    The Iterated Prisoner's Dilemma is a well established framework for
    the study of emergent behaviour. In this paper an extensive numerical
    study of the evolutionary dynamics of this framework are presented.

    Fixation probabilities for Moran processes are obtained for 164
    different strategies.

    To the authors knowledge this is the largest
    such study. It allows for insights about the behaviour and
    performance of strategies with regard to their survival in an
    evolutionary setting.

    Evidence is presented that shows that classical analysis of evolutionary
    dynamics with 2 individuals is misleading. Furthermore, it is shown that
    players with long memories and sophisticated behaviours outperform many
    strategies that perform well in a 2 individual setting (such as zero
    determinant strategies).

\end{abstract}

@@

The Prisoner's Dilemma (PD)~\cite{Flood1958} is a fundamental two person game 
in Game theory. Each player can choose between cooperation (C) or defection 
(D). The decisions are made simultaneously and independently. The payoffs of
the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
\end{pmatrix}$, where $T > R > P> S$ and $2R > T + S$. The PD is a one 
round game, but is commonly studied in a manner where the prior outcomes 
matter, the game then extends to its `iterated'\ form, the Iterated Prisoner's 
Dilemma (IPD).

Since the formulation of the Moran Process in \cite{Moran1957}, this model of
evolutionary population dynamics has been used to gain insights about the
evolutionary stability of strategies in a number of settings. Similarly since
the first Iterated Prisoner's Dilemma (IPD) tournament described in
\cite{Axelrod1980a} the Prisoner's dilemma has been used to understand the
evolution of cooperative behaviour in complex systems.

The analytical models of a Moran process are based on the relative fitness
between two strategies and take this to be a fixed value \(r\) \cite{Nowak}.
This is a valid model for simple strategies of the Prisoner's Dilemma such as to
\textit{always cooperate} or \textit{always defect}. This manuscript provides a
detailed numerical analysis of \textbf{164} complex and adaptive strategies for
the IPD\@. In this case the relative fitness of a strategy is dependent on the
population distribution.

Further deviations from the analytical model occur when interactions between
players are subject to uncertainty. This is referred to as noise and has been
considered in the IPD setting in \cite{Bendor1993, Nowak1993, Wu1995}.

This work provides answers to the following questions:

\begin{enumerate}
    \item What strategies are good invaders?
    \item What strategies are good at resisting invasion?
    \item How does the population size affect these findings?
\end{enumerate}

Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
process. This process is a stochastic birth death process on a finite population
in which the population size stays constant over time. Individuals are
\textbf{selected} according to a given fitness landscape. Once selected, a given
individual is reproduced and similarly another individual is chosen to be
removed from the population. In some settings mutation is also considered but
without mutation (the case considered in this work) this process will arrive at
an absorbing state where the population is entirely made up of a single
individual. The probability with which a given strategy is the survivor is
called the fixation probability. A more detailed analytic description of this
is given in Section~\ref{sec:validation}.

@@

The Moran process was initially introduced in \cite{Moran1957} in a genetic
setting. It has since been used in a variety of settings including the
understanding of the spread of cooperative behaviour. For instance, cancer 
cells \cite{West2016}. Emergence of cooperative behaviour, also includes 
studies in spatial topologies \cite{Nowak2017}. However, as stated before, 
these mainly consider non sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely used setting of the Moran process but in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
looked at in a theoretic framework for a small subset of strategies. 
The subset included memory one strategies, strategies that recall the events 
of the previous round only. In \cite{Press2012}, a set of memory one 
strategies, the zero determinant strategies, were introduced. The ZD\@,
strategies are highly praised and in \cite{Stewart26062012} argued that 
generous ZD strategies are robust against invading strategies. However,
in \cite{Lee2015} machine learning techniques are used to train a strategy 
capable of resisting invasion and also able to invade any memory one strategy. 
Recent work \cite{Hilbe2017} has investigated the effect of memory length on 
strategy performance and the emergence of cooperation but this is not done in 
Moran process context and only considers specific cases of memory 2 strategies.
% TODO Add discussion about ZD strategies and discuss how this corresponds to
% case of N = 2. Include pointing at \cite{Adami2013} which discusses how ZD
% strategies are not fantastic in population dynamics.
% Add \cite{Li2014}

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 164 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD\@. The strategies and simulation frameworks are
automatically tested in accordance to best research software practice. The large
number of strategies are available thanks to the open source nature of the
project with over 40 contributions made by different programmers. Thus by
considering Moran processes with population size greater than 2 we are taking in
to account the effect of complex population dynamics. By considering
sophisticated strategies we are taking in to effect the reputation of a strategy
during each interaction.

Section~\ref{sec:methodology} will explain the methodological approach used,
Section~\ref{sec:validation} will validate the methodology by comparing
simulated results to analytical results. The main results of this manuscript are
presented in Section~\ref{sec:empirical_results} which will present a detailed
analysis of all the data generated. Finally, Section~\ref{sec:conclusion} will
conclude and offer future avenues for the work presented here.

@@

To carry out this large numerical experiment 164 strategies are used from
\cite{axelrodproject}. These include 161 default strategies in the library at
the time (excluding strategies classified as having a long run time and those
that make use of the length of the game) as well as
the following 3 finite state machine machine strategies \cite{Ashlock2006}:

% TODO Include details about the 3 extra FSM strategies.
% Possibly draw pictorial representations?

Appendix~\ref{app:list_of_players} shows all the players in question. More
information about each player can be obtained in the documentation for
\cite{axelrodproject}. There are \input{./tex/num_stochastic.tex}stochastic and
\input{./tex/num_deterministic.tex}deterministic strategies. Their memory
depth is shown in Table~\ref{tbl:memory_depth_count}.

@@

All strategies are paired and these pairs are used in 1000 repetitions of a
Moran process assuming a starting population distribution of \(1, N-1 \),
\((N/2, N/2)\) and \(N-1 , 1\). This is repeated for \(N\) between 2 and 14. The
% TODO Change 14 to 12 if we do not use the 14 case.
fixation probability is then estimated for each value of \(N\).

Note that due to the high computational cost of these experiments, for any given
interaction between two players within the Moran process the outcome is sampled
from a pre computed cache of 1000 match outcomes. This is carried out using
software written for the purpose of this work. This has been
implemented in~\cite{axelrodproject} ensuring that it can be used to either
reproduce the work or carry out further work.
% TODO Perhaps write some pseudo code for this?

Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
the number of outcomes between all strategy pairs.
Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
stochastic matches have less than 788 unique outcomes whilst the maximum number
is 971. This ensures that using a set of cached results from 1000 precomputed
matches is sufficient for the analysis taking place here.

@@

Using this comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
values and the line shows the theoretic value. Note that these are all
deterministic strategies and show a perfect match up between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategies pairs.

@@

This section will outline the data analysis carried out:

\begin{itemize}
    \item Section~\ref{sec:two_individuals} will consider the specific case of
        \(N=2\).
    \item Section~\ref{sec:strong_invaders} will investigate the effect of
        population size on the ability of a strategy to invade another
        population. This will highlight how complex strategies with long
        memories outperform simpler strategies.
    \item Section~\ref{sec:strong_resistors} will similarly investigate the
        ability to defend against an invasion.
    \item Section~\ref{sec:population_size} will investigate the relationship
        between performance for differing population sizes. This highlights the
        importance of considering population dynamics over large populations.
    \item Section~\ref{sec:relative_fitness} will calculate the relative fitness of all
        strategies.
\end{itemize}

@@

The main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
reflect a strategy's ability to invade or resist invasion.
% TODO Perhaps mention that a lot of the research in to training fixation of
% strategies assumes N=2? Is this true?
For \(N=2\) these two cases coincide. Figure~\ref{fig:fixation_heatmap_2} shows
all pairwise fixation probabilities for strategies on the vertical column when
being matched against probabilities on the horizontal column. This is summarised
in Figure~\ref{fig:boxplot_2} and Table~\ref{tbl:summary_top_2}.

\begin{enumerate}
    \item The top strategy is an extortionate Zero determinant
        strategy~\cite{Press2012} with parameters \(l=1\) and \(s=1/4\).
    \item The Collective strategy has a simple handshake mechanism (a
        cooperation followed by a defection on the first move). As long as the
        opponent plays the same handshake and does not defect in the future it
        cooperates. Otherwise it defects for all rounds~\cite{Li2009}.  This
        strategy was specifically designed for Evolutionary processes so it is
        perhaps also not surprising that it does well here.
    \item The finite state machine strategy % TODO Perhaps refer to earlier
        % discussion in the methodology section about these FSM strategies
    \item The Feld strategy is the corresponding strategy submitted to Axelrod's
        first tournament~\cite{Axelrod1980a}: it punishes defections but
        otherwise defects with a random probability that decays over time.
    \item The final strategy in the top five is another extortionate Zero
        determinant strategy~\cite{Press2012} with parameters \(l=p\).
\end{enumerate}

@@

As will be demonstrated in Section~\ref{sec:population_size} \(N=2\)
is a particular case. In the next sections we will pay close attention to
strategies who are strong invaders/resistors and shown diagrammatically in
Figure~\ref{fig:invasion_resistance}.

@@

In this section \(x_i\) will be investigated: the probability of 1 individual of
a given type successfully becoming fixated in a population of \(N - 1\) other
individuals. Figures~\ref{fig:fixation_heatmap_invade} shows these values for
the players along the vertical axis when matched against the players on the
horizontal axis. It can be seen that invasion is in general more challenging for
\(N=7\) and \(N=12\) in comparison to \(N=3\).
%TODO Change this to N=14
This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
showing the median fixation as well as the neutral fixation for each given
scenario.

@@

It can be seen that apart from the Collective strategy, none of the strategies
of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 12\}\). The new
% TODO Change N=12 to N=14
high performing strategies are:

\begin{itemize}
    \item Predator, a finite state machine described in~\cite{Ashlock2006}.
    \item Prober 4, complex strategy with an initial 20 move sequence of
        cooperations and defections~\cite{prison}. This initial sequence serves
        as some kind of handshake.
    \item Remorseful Prober, a strategy that will not immediately retaliate when
        it recognises that the opponent is itself retaliating to a random
        defection~\cite{Li2011}.
    \item  Worse and worse 2: plays tit for tat for 20 moves and then defects
        with with growing probability~\cite{prison}.
    \item Tester: a strategy submitted to the second of Axelrod's tournaments
        \cite{Axelrod1980b}.
        % TODO Check if this list is still correct for N=14
\end{itemize}

As well as noting that the memory length and complexity of these strategies are
quite complex it is interesting to note that none of them are akin to memory one
strategies. Most are not stochastic.

In the next section the performance in terms of \(x_{N-1}\) will be described:
what strategies are particularly good at resisting an invasion.

@@

Figures~\ref{fig:fixation_heatmap_resist} show \(x_{N-1}\)
the players along the vertical axis when matched against the players on the
horizontal axis. It can be seen that as the population size \(N\) increases the
probability of resistance increases.
This information is summarised in Figure~\ref{fig:fixation_boxplot_resist}
showing the median fixation as well as the neutral fixation for each given
scenario.

@@

\begin{itemize}
    \item Collective;
    \item Predator;
    \item Prober 4
\end{itemize}

@@

\begin{itemize}
    \item Handshake: a slightly less aggressive version of the Collective
        strategy \cite{robson1989}. As long as the initial sequence is played
        then it cooperates. Thus it will do well in a population consisting of
        many members of itself: just as the Collective strategy does. However it
        is not aggressive enough to invade other populations.
    \item Winner 21: a strategy that makes it's decision deterministically based
        on 1 round of it's own strategy and 2 of the opponents strategy
        \cite{Mathieu2015}.
\end{itemize}
% TODO Revise this if need be for N=14

Interestingly none of these strategies are deterministic: this is explained by
the need of strategies to have a steady hand when interacting with their own
kind. In essence: acting stochastically increase the chance of friendly fire.

@@

\printbibliography

>>>>

% \usepackage[backend=biber, firstinits=false, backref=false, url=true,
%             isbn=true, style=numeric]{biblatex}
% \addbibresource{./tex/bibliography.bib}

% Title
\title{An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies}
\author{Marc Harper \and Vincent Knight \and Nikoleta E. Glynatsi} % TODO Authors?
\date{}

@@

\begin{abstract}
    The Iterated Prisoner's Dilemma is a well established framework for
    the study of emergent behaviour. In this paper an extensive numerical
    study of the evolutionary dynamics of this framework are presented. Fixation
    probabilities for Moran processes are obtained for 164
    different strategies. We find that players with long memories and
    sophisticated behaviours outperform many strategies that perform well
    in a two player setting.
\end{abstract}

@@

The Prisoner's Dilemma (PD)~\cite{Flood1958} is a fundamental two player game 
used to model a large variety of strategic interactions. Each player can choose
between cooperation (C) or defection (D). The decisions are made simultaneously
and independently. The payoffs of
the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
\end{pmatrix}$, where $T > R > P > S$ and $2R > T + S$. The PD is a one 
round game, but is commonly studied in a manner where the prior outcomes 
matter. This extended form is called the Iterated Prisoner's 
Dilemma (IPD).

The Moran Process \cite{Moran1957} is a model of
evolutionary population dynamics that has been used to gain insights about the
evolutionary stability and fixation of strategies in a number of settings.
Similarly since the first Iterated Prisoner's Dilemma (IPD) tournament described in
\cite{Axelrod1980a}, the Prisoner's dilemma has been used to understand the
evolution of cooperative behaviour in complex systems. Several earlier
works have studied iterated games in the context of the prisoner's dilemma
\cite{Nowak} \cite{Stewart2012}.

This manuscript provides a detailed numerical analysis of \textbf{164}
complex and adaptive strategies for the IPD\@. This is made possible
by the Axelrod library \cite{axelrodproject}, an effort to provide
software for reproducible research for the IPD. The library now contains over 150
parameterized strategies including classics like TitForTat and WinStayLoseShift,
as well as recent variants such as OmegaTFT, zero determinant and other memory one strategies,
strategies based on finite state machines, lookup tables, neural networks,
and other machine learning based strategies, and a collection of novel strategies.
The library can conduct matches, tournaments and population dynamics
with variations including noise and spatial structure.

We present fixation probabilities for all pairs of
strategies in the library, identifying those are effective invaders and
those resistant to invasion, for population sizes $N=2$ to $N=14$.

In particular we address the following questions:
\begin{enumerate}
    \item What strategies are good invaders?
    \item What strategies are good at resisting invasion?
    \item How does the population size affect these findings?
\end{enumerate}

While our results agree with some of the published literature, we find that:

\begin{enumerate}
 \item Zero determinant strategies are not particularly effective for $N > 2$
 \item Long memory strategies are generally more effective than short memory strategies
 \item Complex strategies can be effective
\end{enumerate}

\subsection{The Moran Process}

Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
process, a stochastic birth death process on a finite population
in which the population size stays constant over time. Individuals are
\textbf{selected} according to a given fitness landscape. Once selected, the
individual is reproduced and similarly another individual is chosen to be
removed from the population. In some settings mutation is also considered but
without mutation (the case considered in this work) this process will arrive at
an absorbing state where the population is entirely made up of players of
one strategy. The probability with which a given strategy is the survivor is
called the fixation probability. A more detailed analytic description of this
is given in Section~\ref{sec:validation}.

@@

The Moran process was initially introduced in \cite{Moran1957}. It has since been
used in a variety of settings including the
understanding of the spread of cooperative and non-cooperative behaviour
such as cancer \cite{West2016} and the emergence of cooperative behaviour
in spatial topologies \cite{Nowak2017}. However these works 
mainly consider non-sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely-used setting of the Moran process, rather in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
studied in a theoretical framework for a small subset of strategies. 
The subset included memory one strategies, strategies that recall the events 
of the previous round only.

Of particular interest are the zero determinant strategies introduced in \cite{Press2012}
and highly-praised \cite{Stewart26062012} it was argued that 
generous ZD strategies are robust against invading strategies. However,
in \cite{Lee2015} a strategy using machine learning techniques was
capable of resisting invasion and also able to invade any memory one strategy. 
Recent work \cite{Hilbe2017} has investigated the effect of memory length on 
strategy performance and the emergence of cooperation but this is not done in 
Moran process context and only considers specific cases of memory 2 strategies.
In \cite{Adami2013} it was recognized that many zero determinant strategies do
not fare well against themselves. This is a disadvantage for the Moran process
where the best strategies cooperate well with other players using the same strategy.

% TODO Add discussion about ZD strategies and discuss how this corresponds to
% case of N = 2. Include pointing at \cite{Adami2013} which discusses how ZD
% strategies are not fantastic in population dynamics.
% Add \cite{Li2014}

\subsection{The Axelrod Library}

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 164 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD\@. The strategies and simulation frameworks are
automatically tested to an extraordinarily high degree of coverage in accordance
with best research software practices. The large
number of strategies are available thanks to the open source nature of the
project with over 40 contributions made by different programmers and researchers.

Section~\ref{sec:methodology} will explain the methodological approach used,
Section~\ref{sec:validation} will validate the methodology by comparing
simulated results to analytical results in some cases. The main results of this manuscript are
presented in Section~\ref{sec:empirical_results} which will present a detailed
analysis of all the data generated. Finally, Section~\ref{sec:conclusion} will
conclude and offer future avenues for the work presented here.

@@

To carry out this large numerical experiment, 164 strategies are used from
\cite{axelrodproject}. These include 161 default strategies in the library at
the time (excluding strategies classified as having a long run time and those
that make use of the length of the game) as well as
the following 3 finite state machine machine strategies \cite{Ashlock2006}:

% TODO Include details about the 3 extra FSM strategies.
% Possibly draw pictorial representations?
% Remove the FSM strategies if they don't perform well.

Appendix~\ref{app:list_of_players} shows all the players in question. More
information about each player can be obtained in the documentation for
\cite{axelrodproject}. There are \input{./tex/num_stochastic.tex}stochastic and
\input{./tex/num_deterministic.tex}deterministic strategies. Their memory
depth, defined by the number of rounds of history used by the strategy each round,
is shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if
the strategy uses the entire history of play (whatever its length). For example,
a strategy that utilizes a handshaking mechanism where the opponents actions
on the first few rounds of play determines the strategies subsequent behavior
would have infinite memory depth.

@@

Each strategy pair is run for 1000 runs of the Moran process to fixation
with starting population distributions of $(1, N-1)$,
$(N/2, N/2)$ and $(N-1 , 1)$, for \(N\) from 2 through 14. The
% TODO Change 14 to 12 if we do not use the 14 case.
fixation probability is then empirically computed for each combination of
starting distribution and value of \(N\).

Our software can carry out exact simulations of the Moran process. Since some of
the strategies have a high computational cost or are stochastic, we sample
from a large number of match outcomes for the pairs of players for use in computing
fitnesses in the Moran process. This approach was verified to agree with unsampled
calculations to a high degree of accuracy in specific cases.
% TODO Perhaps write some pseudo code for this?

Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
the number of outcomes between all strategy pairs.
Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
stochastic matches have less than 788 unique outcomes whilst the maximum number
is 971. This ensures that using a set of cached results from 1000 precomputed
matches is sufficient for the analysis taking place here.
% TODO is this true? the distribution also matters, not just the number of outcomes

@@

A neutral strategy will have fixation probability $x_i = i/N$. Alternatively,
we can frame the outcomes in terms of relative fitness. For a strategy
of relative fitness $r$ the fixation probability is well-known to be

\[ x_i = \frac{1 - r^{-i}}{1 - r^{-N}} \]

We can use this formula to compute a value $r_i$ that produces the observed
value $x_i$, noting that for arbitrary strategies the value of this
effective relative fitness is dependent on $i$ and $N$.

Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
values and the line shows the theoretical value. Note that these are all
deterministic strategies and show a perfect match up between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategies pairs.

@@

This section outlines the data analysis carried out:

\begin{itemize}
    \item Section~\ref{sec:two_individuals} considers the specific case of
        \(N=2\).
    \item Section~\ref{sec:strong_invaders} investigates the effect of
        population size on the ability of a strategy to invade another
        population. This will highlight how complex strategies with long
        memories outperform simpler strategies.
    \item Section~\ref{sec:strong_resistors} similarly investigates the
        ability to defend against an invasion.
    \item Section~\ref{sec:population_size} investigates the relationship
        between performance for differing population sizes.
    \item Section~\ref{sec:relative_fitness} calculates the relative fitness of all
        strategies.
\end{itemize}

@@

When $N=2$ the Moran process is effectively a measure of the relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often.

Overall the main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
reflect a strategy's ability to invade or resist invasion; for \(N=2\) these two cases
coincide. Figure~\ref{fig:fixation_heatmap_2} shows
all pairwise fixation probabilities for strategies on the vertical column when
being matched against probabilities on the horizontal column. This is summarised
in Figure~\ref{fig:boxplot_2} and Table~\ref{tbl:summary_top_2}.

\begin{enumerate}
    \item The top strategy is an extortionate Zero determinant
        strategy~\cite{Press2012} with parameters \(l=1\) and \(s=1/4\).
    \item The Collective strategy has a simple handshake mechanism (a
        cooperation followed by a defection on the first move). As long as the
        opponent plays the same handshake and does not defect in the future it
        cooperates. Otherwise it defects for all rounds~\cite{Li2009}.  This
        strategy was specifically designed for evolutionary processes.
    \item The finite state machine strategy % TODO Perhaps refer to earlier
        % discussion in the methodology section about these FSM strategies
    \item The Feld strategy is the corresponding strategy submitted to Axelrod's
        first tournament~\cite{Axelrod1980a}: it punishes defections but
        otherwise defects with a random probability that decays over time.
    \item The final strategy in the top five is another extortionate Zero
        determinant strategy~\cite{Press2012} with parameters \(l=p\).
\end{enumerate}

@@

As will be demonstrated in Section~\ref{sec:population_size} the results for \(N=2\)
differ from those of larger $N$. Hence our results do not concur with the literature
which suggests that Zero Determinant strategies should be effective for larger population
sizes, but we note that those analysis run each match to stationarity, while
our matches run for a fixed number of rounds.

In the next sections we pay close attention to
strategies who are strong invaders/resistors and shown diagrammatically in
Figure~\ref{fig:invasion_resistance}.

@@

In this section we focus on the ability of a mutant strategy to invade: the
probability of 1 individual of a given type successfully becoming fixated in
a population of \(N - 1\) other individuals, denoted by \(x_i\).
Figures~\ref{fig:fixation_heatmap_invade} shows these values for
the players along the vertical axis when matched against the players on the
horizontal axis. For population size $N$, a neutral mutant has fixation
probability $x_1 = 1 / N$. This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
showing the median fixation as well as the neutral fixation for each given
scenario.

@@

It can be seen that apart from the Collective Strategy, none of the strategies
of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 12\}\). The new
% TODO Change N=12 to N=14
high performing strategies are:

\begin{itemize}
    \item Predator, a finite state machine described in~\cite{Ashlock2006}.
    \item Prober 4, complex strategy with an initial 20 move sequence of
        cooperations and defections~\cite{prison}. This initial sequence serves
        as approximate handshake.
    \item Remorseful Prober, a strategy that will not immediately retaliate when
        it recognises that the opponent is retaliating to a random
        defection~\cite{Li2011}.
    \item  Worse and Worse 2: plays Tit For Tat for 20 moves and then defects
        with with growing probability~\cite{prison}.
    \item Tester: a strategy submitted to the second of Axelrod's tournaments
        \cite{Axelrod1980b}.
        % TODO Check if this list is still correct for N=14
\end{itemize}

As well as noting that the memory length and complexity of these strategies are
much greater than one, it is interesting to note that none of them are akin to
memory one strategies. Most are not stochastic.

@@

In addition to identifying good invaders, we also identify strategies
resistant to invasion by other strategies by examining the distribution
of $x_{N-1}$ for each strategy. Note that this is equivalent to
looking at $x_1$ for all opponents.

Figures~\ref{fig:fixation_heatmap_resist} show \(x_{N-1}\)
the players along the vertical axis when matched against the players on the
horizontal axis. This information is summarised in Figure~\ref{fig:fixation_boxplot_resist}
showing the median fixation as well as the neutral fixation for each given
scenario.

@@

\begin{itemize}
    \item Collective
    \item Predator
    \item Prober 4
\end{itemize}

@@

\begin{itemize}
    \item Handshake: a slightly less aggressive version of the Collective
        strategy \cite{robson1989}. As long as the initial sequence is played
        then it cooperates. Thus it will do well in a population consisting of
        many members of itself: just as the Collective strategy does. However it
        is not aggressive enough to invade other populations.
    \item Winner 21: a strategy that makes its decision deterministically based
        on 1 round of its own strategy and 2 of the opponent's strategy
        \cite{Mathieu2015}.
\end{itemize}
% TODO Revise this if need be for N=14

Interestingly none of these strategies are stochastic: this is explained by
the need of strategies to have a steady hand when interacting with their own
kind. In essence: acting stochastically increase the chance of friendly fire.
However we note that it is possible to design a strategy with a ``stochastic
handshake'' \cite{Lee2015}.

@@

% \printbibliography
